\documentclass[11pt]{article}
\usepackage{epsfig}
\usepackage{subfigure}
\usepackage{setspace}
\usepackage{url}

\setlength{\textheight}{8.875in} \setlength{\textwidth}{6.5in}
\setlength{\topmargin}{0.0in} \setlength{\headheight}{0.0in}
\setlength{\headsep}{0.0in} \setlength{\oddsidemargin}{0.0in}

\begin{document}
\pagestyle{empty}
\thispagestyle{empty}

\begin{center}
\textbf{\Large Budget Justification\\(Washington Univ. in St. Louis)}
\end{center}

\subsection*{Personnel}
We request 0.33 month of support for PI Chamberlain and Co-PIs
Ahrens and Gill.
Chamberlain will be responsible for overall project management. Ahrens will
lead the design of prototype catoptric systems, and Gill will guide the
controller design efforts.

\vspace{0.2in}
\noindent
Senior Personnel Iannotti and Jonson-Reid have agreed to consult,
uncompensated, for the purpose of assisting us to identify ways to overcome
urban food deserts as part of the planning process.

\vspace{0.2in}
\noindent
We request 0.75 support for a staff programmer (Dwaraki), who will assist
in implementing the prototype systems.

\subsection*{Travel}
We request travel funds for PI/Co-PIs
to present our work at academic 
conferences and to attend any PI meetings.
Candidate conferences include ACADIA, ICCPS, RTAS, etc.
We will also ensure that at least one PI/Co-PI is
at any annual PI meetings that are arranged by NSF. 

\subsection*{Indirect costs}
Indirect costs are requested at Washington University's standard rate of
57.5\% of MTDC (starting 7/1/2020).

\end{document}
